Stack Safety is a Security Property

### 2021-04-17 tex/main.tex
WBCF: C returns to B (not A) in A -> B -> C :-)

\paragraph{Well-bracketed control flow.} Together,
integrity and confidentiality protect a caller's data until its callee
returns to it. However, it is possible that an intermediate caller is not
returned {\em to}, but rather returned {\em past}, to some ancestor caller!
For example, function $A$ calls function $B$, which in turn calls $C$, which
returns directly to $A$ by resetting the stack pointer to $A$'s stack frame
and branching to the address after the call from $A$ to $B$.  Strictly
speaking, this is not an information-flow violation, since neither $A$'s nor
$B$'s stack frames are improperly read or written by $C$.  But it is still
arguably unsafe in general.  For example, suppose that $B$'s continuation
after the call to $C$ takes $C$'s result, doubles it, and returns this to
$A$.  If $A$'s correct behavior after the call to $B$ returns depends on the
result it receives being a even number---i.e., $A$ is trusting that $B$'s
continuation will execute after $C$ returns, perhaps because $A$ and $B$ are
written by the same person while $C$ is an untrusted library---then $C$ can
cause it to behave incorrectly, possibly even insecurely, by returning an
odd result directly to $A$.
%
Thus, a formal definition of safe use of the stack should include the
condition that calls and returns are {\em well bracketed}, e.g., $C$ should
only return to $A$.  This is what \citet{Skorstengaard+19b} describe
as \emph{well-bracketed control flow (WBCF)}.

>>>>

\paragraph{Well-bracketed control flow.} Together,
integrity and confidentiality protect a caller's data until its callee
returns to it. However, it is possible that an intermediate caller is not
returned {\em to}, but rather returned {\em past}, to some ancestor caller!
For example, function $A$ calls function $B$, which in turn calls $C$, which
returns directly to $A$ by resetting the stack pointer to $A$'s stack frame
and branching to the address after the call from $A$ to $B$.  Strictly
speaking, this is not an information-flow violation, since neither $A$'s nor
$B$'s stack frames are improperly read or written by $C$.  But it is still
arguably unsafe in general.  For example, suppose that $B$'s continuation
after the call to $C$ takes $C$'s result, doubles it, and returns this to
$A$.  If $A$'s correct behavior after the call to $B$ returns depends on the
result it receives being a even number---i.e., $A$ is trusting that $B$'s
continuation will execute after $C$ returns, perhaps because $A$ and $B$ are
written by the same person while $C$ is an untrusted library---then $C$ can
cause it to behave incorrectly, possibly even insecurely, by returning an
odd result directly to $A$.
%
Thus, a formal definition of safe use of the stack should include the
condition that calls and returns are {\em well bracketed}, e.g., $C$ should
only return to $B$.  This is what \citet{Skorstengaard+19b} describe
as \emph{well-bracketed control flow (WBCF)}.
